---
title: "Activity 12 - The Taylor Swift Effect?"
author: "STS 2300"
date: 'Updated: 2026-04-19'
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**As a reminder, activities are marked "Complete" or "Incomplete" and contribute to your overall grade. You must show an honest attempt for the required portions (i.e., this section).**

**This is a shorter activity, so there are no sections listed as Optional. Instead, this entire activity is considered Required.**

Below are the packages you will need for this activity. If you use other packages, you can add them here.

```{r, message = FALSE}
library(ggplot2)
library(infer)
```

---

According to a [People.com](https://people.com/travis-kelce-taylor-swift-improved-performance-nfl-8379432) article from fall 2023, Travis Kelce had been performing better when Taylor Swift attended his football games. From the article, Travis Kelce's brother says to him:

> “When T Swift is at the game, you are averaging 99 yards and when you are left with only your friends and remaining family there, you are at 46.5 yards a game.”

We might wonder if Taylor Swift's presence makes Travis Kelce perform better or if this is just random variation that people are talking about.

The code below will read in data for Travis Kelce during the 2023 NFL season. We will focus on two variables: `Rec_Yards` (how many receiving yards he had in the game) and `Swift_Attend` (whether Taylor Swift attended that game).

```{r}
kelce <- read.csv("https://raw.githubusercontent.com/nbussberg/STS2300-Spring2026/refs/heads/main/Data/kelce_stats_23.csv")
```

--- 

1. Step 1 - What are the null and alternative hypotheses for the claims being made here?

$H_0$:

$H_a$:

<br>


2. Step 2 - Calculate an appropriate statistic for this data. In addition, make a graph showing Kelce's receiving yards with and without Taylor Swift in attendance. (Note: Want to make your graph extra fancy? Consider using the [`tayloRswift` package.](https://cran.r-project.org/web/packages/tayloRswift/readme/README.html))

```{r}

```

**Statistic:**


<br>


3. Step 3 - Let's generate a null distribution to explore what Travis Kelce's receiving yards would look like in a world where Taylor Swift had no impact on his performance. Graph your null distribution (with your p-value shaded). Calculate the p-value as well.

```{r}

```

**p-value = **

<br>


4. Step 3 - Briefly describe how the null distribution is created using permutation. (Hint: Imagine that you have slips of paper with the number of yards for each game in front of you. How would you use those to create the null distribution?)

**Answer:**

<br>


5. Step 4 - Use your p-value to write a conclusion for your hypothesis test in context of this example.

**Conclusion:**


