---
title: "Activity 06 - Simple Linear Regression Practice"
author: "STS 2300"
date: 'Updated: 2026-03-15'
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

We will use the following R packages for this activity.

```{r, message = FALSE, warning = FALSE}
library(ggplot2)
library(Lock5Data)
```

---

For this activity, we'll use a dataset called `RestaurantTips` from the `Lock5Data` R package. The data was collected by the owner of a bistro in New York and contains 157 bills at the restaurant over a two week period. Let's explore the relationship between the size of the bill, called `Bill`, and the size of the tip, called `Tip`. Both variables are measured in dollars.

I'm going to read the data into R and call it `tips` to shorten the name a bit.

```{r}
tips <- RestaurantTips
```


# Required Section

**As a reminder, activities are marked "Complete" or "Incomplete" and contribute to your overall grade. You must show an honest attempt for the required portions (i.e., this section).** 



1. Make a scatterplot comparing the bill size and the tip size. (Optional: Consider adding a theme and making the labels nicer with `labs()`). Think carefully about which variable is the response and the explanatory, as well as on which axis each should be plotted.

```{r}

```

<br>


2. Let's use R to calculate a simple linear regression line for this data. In the space below the R chunk, I've used R Markdown's math mode to show you how you can write the general formula. Update this formula to write the equation for your line. You will just need to replace $b_0$ and $b_1$ with the numbers from your equation. You should also either replace y and x with the variable names or define the variables in another line.

```{r}

```

**Formula:** $\hat{y} = b_0 + b_1 * x$

<br>


3. Suppose you're a server at the restaurant and someone has just spent \$23.70 on a meal. How much would you predict their tip would be?

```{r}

```

**Prediction =**

<br>


4. There was one person in the dataset who actually did have a bill of \$23.70. They left a \$10 tip. What would be the residual for that observation?

```{r}

```

**Residual =**

<br>


5. You can  add a simple linear regression line to your scatterplot by adding `geom_smooth(method = "lm", se = FALSE)` as another layer to your ggplot object. Try this out below. Can you find the observation whose residual we just calculated on the graph? (Note: You will need to respecify your x and y aesthetics in `geom_smooth()` or move them to the `ggplot()` function instead.)

```{r}

```

<br>



6. Does your estimated slope make sense based on what you know about tipping?

**Answer:**

<br>


7. Use the `summary()` function on the object created by the `lm()` function. Find the R-squared value in the output and write a sentence interpreting it.

```{r}

```

**R-squared =**

**Interpretation:**


---

# Optional Section

**This section is not required to receive a mark as Complete for this activity.** 

Investigate how well the size of the bill can help predict the tip percentage (`PctTip`).

* Make a scatterplot. What is the relationship between the two variables? How does it compare to what we saw when we compared bill size to tip size (both in terms of dollars).


* Calculate a simple linear regression line and interpret the estimated intercept and estimated slope.
