---
title: "Activity 14 - Practicing Hypothesis Tests for Differences"
author: "STS 2300"
date: 'Updated: 2026-04-25'
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Below are the packages you will need for this activity. If you use other packages, you can add them here.

```{r, message = FALSE}
library(ggplot2)
library(infer)
library(dplyr)
```

---

**To have this activity marked as "Complete"**: You need to complete **either** Part 1 (hypothesis test for difference in $p$) or Part 2 (hypothesis test for difference in $\mu$). I encourage you to attempt both, but only one is required for this activity. However, if you attempt both, that can be factored into our end-of-semester discussion on your grade. If you only choose one, focus on the interval (means or proportions) that you feel like you need most practice with.

Which Part(s) did you complete? ____
---

# Part 1 - COVID-19 Antibodies

The example for this activity comes from a [2020 New York Times article](https://www.nytimes.com/2020/08/19/health/coronavirus-fishing-boat.html) about a ship that had a coronavirus outbreak while at sea. This was before COVID-19 vaccines had been developed and at a time when people were still learning basic information about the virus. Before setting sail, the crew had been tested for COVID-19 antibodies and, 3 of the 120 sailors had these antibodies while the other 117 did not. Below is a quote from the article.

> The three sailors confirmed to have neutralizing antibodies did not test positive for the virus during the course of the study; 103 of the remaining 117 became infected. "These numbers may be small, but they’re highly significant", Dr. Greninger said.

We will conduct a hypothesis test to see if we can see what Dr. Greninger means when he says these results are "highly significant".

<br>


1. Step 1 - How could we set up our hypotheses based on our likely question of interest? Try doing this both in symbols and in words.

**In symbols...** 

$H_0$:

$H_a$:

**Parameter definitions:**


**In words...**

$H_0$:

$H_a$:

<br>


2. Step 2 - The data is mentioned at the top of this activity. I've included code to read it into R below. Create a graph displaying the data in relation to our question of interest and calculate an appropriate statistic for this question.

```{r}
ship <- data.frame(antibodies = c(rep("yes", 3), rep("no", 117)),
                   infected = c(rep("no", 17), rep("yes", 103)))
```

**Statistic:**

<br>


3. Step 3 - Create a null distribution and visualize it with a p-value shaded in. Then calculate the p-value.

```{r}

```

**p-value = **

<br>


4. Step 4 - Write a formal conclusion for this example.

**Conclusion:**

<br>


---

# Part 2 - Revisiting Fidget Spinners Example

We previously looked at some data where people used fidget spinners and researchers measured their attention and memory. Suppose we want to compare the attention score between people who are near a fidget spinner (but not the one using it) and people with no spinner present. We suspect that those without a spinner present might have a higher attention score. (Use $\alpha = 0.05$ for your significance level.)

<br>

5. **Step 1** - Write out the appropriate hypotheses for this problem. Define any parameters below.

$H_0:$

$H_A:$

**Define parameter(s)**

<br>


6. **Step 2** - Below is code to read in the data and to remove the third group (those actively using a spinner). Generate a graph to view the data and then calculate an appropriate statistic to summarize the data for these hypotheses.

```{r}
fidget <- read.csv("https://raw.githubusercontent.com/nbussberg/STS2300-Spring2026/refs/heads/main/Data/fidget_spinners.csv") |> 
  filter(Condition != "Spinner")
```

**Statistic:**

<br>


7. **Step 3** - Use the `infer` package to generate a null distribution. Visualize your p-value on the distribution and calculate the p-value. 

```{r}

```

**p-value =**

<br>


8. **Step 4** - Write a conclusion for your hypothesis test based on the p-value.

**Conclusion:**



