---
title: "Activity 11 - Practicing with Intervals for Differences"
author: "STS 2300"
date: 'Updated: 2026-04-19'
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Below are the packages you will need for this activity. If you use other packages, you can add them here.

```{r, message = FALSE}
library(ggplot2)
library(infer)
library(dplyr)
```

---

**To have this activity marked as "Complete"**: You need to complete **either** Part 1 (interval for difference in means) or Part 2 (interval for difference in proportions). I encourage you to attempt both, but only one is required for this activity. However, if you attempt both, that can be factored into our end-of-semester discussion on your grade. If you only choose one, focus on the interval (means or proportions) that you feel like you need most practice with.

Which Part(s) did you complete? ____

---


# Part 1 - Fidget spinners and attention

A study looked at the effect that fidget spinners have on attention and memory. You can read an article about it [here](https://www.psypost.org/2019/11/study-finds-using-a-fidget-spinner-can-impair-memory-and-attention-54904) or look at the research paper [here](https://onlinelibrary.wiley.com/doi/full/10.1002/acp.3610) if you're interested.

The researchers wanted to know how attention might differ between people using and not using a fidget spinner. The code below will read data from the study directly into R and subset the data to remove a control group where no fidget spinner was used. This leaves us with two groups in the `Condition` variable: "Spinner" (actively using a fidget spinner) and "Spinner Present" (near someone who was using a fidget spinner).

```{r}
fidget <- read.csv("https://raw.githubusercontent.com/nbussberg/STS2300-Spring2026/refs/heads/main/Data/fidget_spinners.csv") |> 
  filter(Condition != "No Spinner")
```

<br>


1. Create a graph that can be used to explore how `AttentionScore` differs between people using a fidget spinner and people near someone using a fidget spinner. 

```{r}

```

<br>


2. Calculate a difference in sample mean attention scores between the two groups. Use "Spinner" - "Spinner Present" as the order of subtraction. Write a sentence about what the value you get means in context of this example. 

```{r}

```

**Sentence about difference in sample means:**



<br>


3. Generate a bootstrap distribution to better understand sampling variability in your estimate. Make a histogram of this distribution. (Note: The `set.seed()` line will ensure we get the same result each time we knit our document. You should replace the number with a number of your choosing.)

```{r}
set.seed(92520)

```

<br>


4. Calculate a confidence interval for the difference in population means that uses your bootstrap distribution. Write your interval below. (Note: I didn't specify a confidence level, so you can choose one)

```{r}

```

**CI:**

<br>


5. Based on your results, what takeaways can we make (or not make) about the impact of fidget spinners on attention?

**Answer:**

<br>


6. For practice, make a theory-based confidence interval for this example as well.

```{r}

```

**CI:**

<br>


---


# Part 2 - Airbnb Discrimination

The code below will read a data frame into R from a study on potential discrimination by Airbnb hosts. In the experiment, researchers sent requests to Airbnb hosts asking to stay at their properties. The only difference on each request was the name that was used. Researchers chose names that were predominantly associated with certain genders and races (determined in a separate study) and randomly assigned a name to each request. They then recorded whether or not the host gave a positive response indicating the person could stay there. 

Our goal will be to determine the difference in proportion of positive responses given by hosts who received a request from a predominantly Black name versus a predominantly white name.

```{r}
airbnb <- read.csv("https://raw.githubusercontent.com/nbussberg/STS2300-Spring2026/refs/heads/main/Data/airbnb.csv")
```

<br>


7. Make a bar graph (using `geom_bar()`) to compare the proportion of positive responses between the two races used in this study. (Note: You want your variable that creates groups (`Race`) to go on the x-axis and your variable of interest (`Response`) to map to fill. Use the `position = "fill"` argument inside `geom_bar()` to get a graph comparing proportions.)

```{r}

```


<br>


8. We can calculate point estimates by writing code for a bootstrap distribution but leaving out the `generate()` argument (i.e., only using `specify()` and `calculate()`). Calculate a difference in sample proportions in this way and explain what the value you get means in this context.

```{r}

```

**Answer:**

<br>


9. Write code to generate a bootstrap distribution. You can reuse your code from the previous question and add in a `generate()` line between `specify()` and `calculate()`. (Note: remember to set a seed)

```{r}

```


<br>


10. Generate a 95% confidence interval using your bootstrap distribution.

```{r}

```

**95% CI:**

<br>


11. As practice, calculate a 95% theory-based interval based on this data.

```{r}

```

**95% CI:**
