---
title: "Activity 13 - Practicing Hypothesis Tests for Single Values"
author: "STS 2300"
date: 'Updated: 2026-04-25'
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Below are the packages you will need for this activity. If you use other packages, you can add them here.

```{r, message = FALSE}
library(ggplot2)
library(infer)
library(dplyr)
```

---

**To have this activity marked as "Complete"**: You need to complete **either** Part 1 (hypothesis test for $p$) or Part 2 (hypothesis test for $\mu$). I encourage you to attempt both, but only one is required for this activity. However, if you attempt both, that can be factored into our end-of-semester discussion on your grade. If you only choose one, focus on the interval (means or proportions) that you feel like you need most practice with.

Which Part(s) did you complete? ____

---

# Part 1 - Fan Attendance and Home Field Advantage

Let's suppose that we're interested in studying the concept of home field advantage in Major League Baseball during the 2020 season when fan attendance was restricted due to COVID-19. If there's no such thing as home field advantage, the home team will win just as often as the away team (half the time). If there *is* an advantage to the home team, they will win over half the time. To carry out this test, use a significance level of $\alpha = 0.05$.


<br>


1. **Step 1** - Write out appropriate null and alternative hypotheses below. Define $p$ for this specific example.

**$H_0:$**

**$H_a:$**

**p =**

<br>


2. **Step 2** - The code below will read data from the 2020 MLB season into R. We will consider this to be a random sample of the *possible* games that could have been played without fans. Create a graphical and numeric summary of this data in context of our example. (Note: We are interested in the `HomeWon` variable and how often it is `TRUE`. The variable has been converted from logical to character to prevent issues with the `infer` package.)

```{r}
mlb <- read.csv("https://raw.githubusercontent.com/nbussberg/STS2300-Spring2026/refs/heads/main/Data/mlb_2020.csv") |> 
  mutate(HomeWon = as.factor(HomeWon))
```

$\hat{p} =$

<br>


3. **Step 3** - Use the `infer` package to create a null distribution and shade in your p-value on the picture. Then calculate the p-value. Remove `eval = FALSE` when you're ready to run your code.

```{r, eval = FALSE}
set.seed()
mlb_null <- mlb |> 
  specify() |> 
  hypothesize() |> 
  generate() |> 
  calculate()
```

**p-value = **

<br>


4. **Step 4** - Write a formal conclusion based on your p-value.

**Conclusion: **

<br>


6. Try using the `prop.test()` function to carry out a theory-based hypothesis test. Do you get similar results?

```{r}

```

<br>



---

# Part 2 - Prius Mileage

Suppose Toyota is claiming that their newest Prius Prime model gets over 100 miles per gallon on average. A car review website plans to test this claim. (Use $\alpha = 0.10$ for your significance level)

<br>


7. **Step 1** - Write out the appropriate hypotheses for this problem. Define any parameters below. (Note: You will not be using $p$ in this example.)

$H_0:$

$H_A:$

**Define parameter(s):**

<br>


8. **Step 2** - Gather and summarize data

The car review website has gathered data from 19 Prius Prime owners. The `average_mpg` variable is what each owner reported as their average miles per gallon over the past month. Below is the code to read in this data. 

Generate a graph to view the data and then calculate an appropriate statistic to summarize the data in relation to these hypotheses. 

```{r}
prius <- read.csv("https://www.openintro.org/data/csv/prius_mpg.csv")
```

**Statistic:**


<br>


9. **Step 3** - Use the `infer` package to generate a null distribution. Visualize your p-value on the distribution and calculate the p-value.

```{r}
# Remember to set a seed
```

**p-value =**

<br>


10. **Step 4** - Write a conclusion for your hypothesis test Make sure that you address each of the important elements mentioned in class.

**Conclusion:**


<br>



11. Practice write code to use an appropriate function to calculate a p-value for a theory-based test for this example.

```{r}

```

